%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\usepackage{geometry}
\geometry{left=0.5in, right=0.5in, top=0.7in}


% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{1.75in}
%\setlength{\hintscolumnwidth}{0cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Saverio V.}{Miller}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{6419 Pontiac Dr, Indian Head Park, IL 60525 }{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-15mm}

\begin{center}
\begin{tabular}{ c c c c }
 %\faGlobe\enspace mysite.me & \faEnvelopeO\enspace xxxx@swarthmore.edu & \faGithub\enspace yourgithub & \faMobile\enspace 123-456-7891\\ 
 \faEnvelopeO\enspace saveriovmiller@gmail.com & \faMobile\enspace 708-244-0625
\end{tabular}
\end{center}

\vspace*{-8mm}

\section{EDUCATION}
{\customcventry{Expected Graduation: May 2027}{BS in Computer Science - Machine Intelligence Track - Statistics Minor}{Purdue University}{West Lafayette, IN}{}{\vspace*{1mm}\textbf{Relevant Coursework:} Python Programming, Object Oriented Programming in Java, Programming in C, Discrete Structures, Tools (GitHub, VIM, UNIX/LINUX), Calculus 1-3, Linear Algebra, Data Structures and Algorithms, Computer Architecutre, Probability, Machine Learning and Data Mining}}


\vspace*{-2mm}
\section{EXPERIENCE}

{\customcventry{Summer 2024}{Software Engineering Intern}{Sims Lifecycle Services}{West Chicago, IL}{}
{\begin{itemize}
  \item Utilized Azure Open AI's machine learning model to develop a .NET API and Angular app that drastically improved warehouse efficiency by scanning pieces of technology and automatically storing data in the cloud, increasing the average amount of data collected by 50\% and eliminating the need for manual entry. 
  \item Developed a GRPC API and accommodating Azure Queue to periodically send product data to the client.
  \item Worked directly with clients to develop a solution that looked and worked best for both parties.
\end{itemize}
}

{\customcventry{Mar 2024 - Present}{Leadership, Allyship, and Mentorship Program}{Deloitte}{Remote}{}
{\begin{itemize}
  \item Accepted from a large pool of students to participate in a small scale college cohort, and a large national cohort with 240 students from 40 top schools.
  \item A cohort-driven mentorship program with a focus on building meaningful connections, developing leadership skills, cultivating professional confidence, and an introduction to consulting.
  \item Paired with junior- and senior-level mentors for career consulting, network building, and interview prep.
\end{itemize}
}

}

{\customcventry{Summer 2023}{Undergraduate Summer Intern}{\textbf{University of Notre Dame, Computational Hydraulics Lab}}{Notre Dame, IN}{}
{\begin{itemize}
  \item Computationally modeled tides using MATLAB on the global scale for the National Oceanic and Atmospheric Administration. Sent operational model to super computer for processing and use by the coast guard.
  \item Analyzed data set trends and model performance to identify errors and root cause. Reasons for errors include bathymetric data sets, frictional datasets, model resolution, etc. 
  \item Remapped the global scale model to improve overall accuracy by 5\%  
\end{itemize}
}
}

{\customcventry{Jan 2022 - Apr 2023}{Web Developer}{\textbf{Barefoot Bay}}{Chicago, IL}{}
{\begin{itemize}
  \item Collaborated with company owners to develop and oversee an e-commerce website using a custom WordPress theme in HTML and CSS, with some of their specific needs being inventory management and custom product selection.
  \item Expanded company reach from local stores to national sales.
\end{itemize}
}
}





\vspace*{-2mm}
\section{PROJECTS}

{\customcvproject{Restaurant Recommendation App - Machine Learning, React, Flask}{}
  {\begin{itemize}
    \item Implemented a machine learning model to select restaurants based on variables including price and health.
    \item Used the model to create an application that pulls local restaurants based on the users location.
    \item Worked in react to develop the front end and flask to develop a lightweight back end in Python.
  \end{itemize}
  }
}

{\customcvproject{Digital Marketplace with Messaging - Java, API}{}
{\begin{itemize}
  \item Used Java to create a digital store program that allows users to log in, add products for selling, and purchase products.
  \item Implemented an API for seamless client, server interaction to save and process data with SQLite.
\end{itemize}
}

{\customcvproject{Robotics Exploration - C++}{}
{\begin{itemize}
  \item Worked with sensors and self-developed PID control and odometry algorithms, concurrently, to automate and allow for user and automatic control a of Vex robot, learning fundamental principles of real world robotics.
\end{itemize}
}
}



\vspace*{-2mm}
\section{SKILLS}
\begin{minipage}{\maincolumnwidth}%
	\small{
        \textbf{Languages:} Python, Java, C, C++, C\#, HTML/CSS, JavaScript, TypeScript \newline
        \textbf{Frameworks:} Node.js, Angular, React, .NET, Flask \newline
        \textbf{Tools:} Git, Unix, Azure Functions, Azure Databases, Azure Open AI, SQL, DevOps \newline
        \textbf{Concepts:} Machine Learning, Software Engineering, Robotics, Frontend, Backend, Agile Methodologies
}\end{minipage}%
      
}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
